|

### 2022-06-23 docs/rmd/paper.Rmd
autogit

>>>>

<!-- Vorgehen --->
Section 2 will give a brief summary and discussion of topic related scientific research. Section 3 describes the design of the experiment as well as GP specific implementation. The detailed evaluation of all relevant results and the summarized conclusions are given in section 3 and 4. Section 5 addresses limitation and open questions of this research project.

### 2022-06-23 docs/rmd/paper.tex
autogit

>>>>

Section 2 will give a brief summary and discussion of topic related
scientific research. Section 3 describes the design of the experiment as
well as GP specific implementation. The detailed evaluation of all
relevant results and the summarized conclusions are given in section 3
and 4. Section 5 addresses limitation and open questions of this
research project.
